 

### 2021-08-25 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

![**Figure `r fig_schematic`. Schematic summarizing vertical gradients in forests with dense canopies during daytime growing season conditions.** Patterns summarized here tend to be weaker, or sometimes reversed, under more open canopies, when canopy trees are seasonally deciduous, or at nighttime. Arrows indicate direction of increase, with double-pointed arrows indicating that observations have shown increases both higher and lower in the canopy  [Issue #27](https://github.com/EcoClimLab/vertical-thermal-review/issues/27). ](schematics/Schematic figure 1.png)

>>>>

![**Figure `r fig_schematic`. Schematic summarizing vertical gradients in forests according to (1) biophysical environment, (2) leaf temperature, (3) leaf traits, (4) leaf metabolism, and (5) whole-tree and ecosystem ecology. Abbreviations are as follows: VPD: vapor pressure deficit;  Tleaf - Tair: leaf-to-air temperature difference; LMA: leaf mass per area, VAZ: violaxanthin, antheraxanthin and zeaxanthin concentrations, VOC: volatile organic compounds; temp sensitivity: temperature sensitivity; ET: evapotranspiration, GPP: gross primary productivity.** Here, we summarize conditions in dense canopies during growing season and daytime conditions; patterns tend to be weaker, or sometimes reversed, in more open canopies, when canopy trees are seasonally deciduous, or at nighttime. Arrows indicate direction of increase, with double-pointed arrows indicating that observations have shown increases both higher and lower in the canopy [Issue #27](https://github.com/EcoClimLab/vertical-thermal-review/issues/27). ](schematics/Schematic figure 1.png)
